Milestone 2: Core results 01

### 2023-01-27 R_codeP01/reports/MS2_report02.Rmd
worked on XGboost and rapport

# Major goal
1. Predict outcome of cancer treatment with genetic profile as independent features
2. Features selection

# Data
Clinical trail on breast cancer using two different drug combination

# Evaluation
Preliminary experiments (on given data set) showed instability in prediction and feature selection between bootstrap samples. A more thorough evaluation is conducted. Two levels of evaluation is planed:

@@

# Models
## Lasso
## Post Lasso
## Ridge
## Elastic Net
## Boosting with stumps as base learner

>>>>

<!-- ```{r echo=FALSE}  -->
<!-- knitr::opts_chunk$set(echo=FALSE)  -->
<!-- ``` -->

```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```
# Data
Two clinical trails on breast cancer (advanced HR+/HER2- and HER2-E breast cancer) using two different drug combination
## Trail 1
Two treatments which differ with respect to drug combination 
- Target: ribociclib and endocrine therapy (letrozole)
- Chemotherapy: doxorubicin, cyclophosphamide and paclitaxel. 
approx. 50 patients in each group.
Endpoints: proliferation score, ROR score

## Trail 2
The primary objective of this study is to compare two cdk4/6 targeted drugs (Palbociclib, n=36; Abemaciclib, n=3 in combination with endocrine therapy (tamoxifen, fulvestrant or aromatase inhibitors,  I think?)

Endpoints: progression free survival (months), OS?, and status of the two former (dont know what that means)

# Major goal
1. Find best model to predict outcome of cancer treatment with genetic profile as predictive features
2. Features selection in order to understand cancer biology

# Major challanges
Preliminary experiments (on trail 1) showed instability in prediction and feature selection between bootstrap samples og Lasso. I believe this is a classical problem of high-dim data?

# Approch
Test all thinkable models to see if some is surperior

# Evaluation of models
Two levels of evaluation is scheduled:

@@

# Models
## Lasso
## Post Lasso
## Ridge
## Elastic Net
## Boosting with stumps as base learner
### - mboost
### - xgboost
## Feature selecting ensemble model
